---
title: "Fire behavior metrics case use"
author: "SIG"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Fire modeling absolute metrics exploration example

The full dataset includes multiple outcome metrics for 27 scenarios (with different grouping factors, such as treatment priority, intensity, type) at four different time points (Year 2024, 2029, 2034, 2039) in four different regions. There are a great number of variations and combinations that the data can be summarized by and visualized. 

In this example, we are using a datacube with South Coast (SC) and Central Coast (CC) region results. 

```{r library}
#First, we will import the R library packages that we will need.

### Libraries -------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  #for plotting map
  sf,
  ggspatial,
  viridis,
  scales)
```

## Single Year: 2039

Initially, we will select a single year, 2039, to explore. 

```{r hiddenresimport, include=FALSE, echo=FALSE}
#run but not show
res_orig <- read_csv(file.path("..",
                               "..",
                               "results",
                               "datacube", 
                               "datacube_interim_SNSCCC_20240617.csv")) %>% 
  mutate(HUC12 = as.character(HUC12)) %>% 
  filter(Region %in% c("SC", "CC"))

#plot dimensions for priority + txtype facets
pt_width <- 6
pt_height <- 7

```

```{r resimport, eval=FALSE}
#read in data
res_orig <- read_csv("datacube_SC_CC.csv") %>% 
  mutate(HUC12 = as.character(HUC12))

```

```{r yr2039}

#Set a factor order so that graphs show in this order
# Want priority order: "Fire", "WUI", "Hybrid"
# Want intensity order: "500k", "1m", "2m"

res <- res_orig %>% 
  #For graphing in the correct order
  # make factor with set order (priority)
  mutate(Priority = as.factor(Priority),
         Priority = forcats::fct_relevel(Priority,
                                         "Fire", "WUI", "Hybrid"),
         #Make factor with set order (intensity))
         TxIntensity = as.factor(TxIntensity),
         TxIntensity = forcats::fct_relevel(TxIntensity,
                                            "500k", "1m", "2m"))

#Filter to single year
res2039 <- res %>% 
  filter(Year == 2039)

```

Suppose we are interested in comparing the difference between the different intensity scenarios: 500k and 2m (2.3 million). We can filter our dataset twice times, once for each intensity group. We rename the outcome metrics to reflect what intensity the scenario was. 

```{r intensity}

res2039_500k <- res2039 %>% 
  filter(TxIntensity == "500k") %>% 
  rename(expBurn_500k = expBurn, 
         expFlame_500k = expFlame,
         expAcf_500k = expPcActive)

res2039_2m <- res2039 %>% 
  filter(TxIntensity == "2m") %>% 
  rename(expBurn_2m = expBurn, 
         expFlame_2m = expFlame,
         expAcf_2m = expPcActive)

```

Then we will join our different intensity tables with each other, careful to match on HUC and all other scenario-defining variables. We want to make sure we are comparing e.g. ```HUC A - Fire Priority - trt1 type - 2.3 m``` to ```HUC A - Fire Priority - trt1 type - 500k``` (i.e. only the intensity is different). 

```{r intensityjoin}

res2039_jt <- res2039_500k %>% 
  left_join(res2039_2m, by = join_by(HUC12, Region, Priority, TxType)) 

#selecting only the relevant fields for convenience
res2039_trim <- res2039_jt %>% 
  dplyr::select(HUC12, Region, Priority, TxType, 
                expBurn_500k, expBurn_2m,
                expFlame_500k, expFlame_2m,
                expAcf_500k, expAcf_2m)

```

Now suppose we are interested in comparing the 500k intensity and 2.3 million intensity. We can plot a joint distribution plot (scatter plot) of the 500k expected burned acres against the 2.3 million intensity expected burned acres. We can also do the same for other metrics, such as the expected total flame index.  

The x-axis is the expBurn value of the 500k intensity for each HUC-priority-type combination, and the y-axis would be the expBurn for the matching HUC-priority-type combination for the 2.3 million intensity level. Adding a 1:1 relationship line visually shows where the expBurn values are equal (i.e. the treatment intensity change did not have an effect). Adding a trend line (linear regression) of the observed expBurn values would show if the increase in intensity caused a change in expBurn values - when the slope of the trend line is less than the 1:1 relationship, the increase in intensity caused a decrease in expBurn. 


```{r overall, out.width="75%"}
#overall expBurn
plot_yr2039_expBurn_overall <- ggplot() + 
  geom_point(data=res2039_trim, 
             aes(x=expBurn_500k, y=expBurn_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) + 
  stat_smooth(data=res2039_trim,
              aes(x=expBurn_500k, y=expBurn_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE, 
              fullrange = TRUE) + 
  labs(title="Year 2039: Expected Burned Acres",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_expBurn_overall

#overall expFlame
plot_yr2039_expFlame_overall <- ggplot() + 
  geom_point(data=res2039_trim, 
             aes(x=expFlame_500k, y=expFlame_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) + 
  stat_smooth(data=res2039_trim,
              aes(x=expFlame_500k, y=expFlame_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE, 
              fullrange = TRUE) + 
  labs(title="Year 2039: Flame Index",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") + 
  theme_bw() +
  theme(aspect.ratio = 1)
plot_yr2039_expFlame_overall

```

We see that in 2039, increasing the intensity does reduce expBurn and expFlame overall (the blue trend line slope is less than the black 1:1 relationship line).

There are many factors that we would like to consider, and we can begin to separate out plots to look at different aspects. The above plot includes multiple regions (SC and CC here), all priorities, and all treatment types.

For example, this is the same expBurn and expFlame plots as above, but faceted (grouped and separated) by region.

```{r region, out.width="75%"}
#region
plot_yr2039_expBurn_reg <- ggplot() +
  geom_point(data=res2039_trim,
             aes(x=expBurn_500k, y=expBurn_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) +
  stat_smooth(data=res2039_trim,
              aes(x=expBurn_500k, y=expBurn_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE,
              fullrange = TRUE) +
  labs(title="Year 2039: Expected Burned Acres",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") +
  facet_wrap(~Region) + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_expBurn_reg

plot_yr2039_expFlame_reg <- ggplot() +
  geom_point(data=res2039_trim,
             aes(x=expFlame_500k, y=expFlame_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) +
  stat_smooth(data=res2039_trim,
              aes(x=expFlame_500k, y=expFlame_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE,
              fullrange = TRUE) +
  labs(title="Year 2039: Flame Index",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") +
  facet_wrap(~Region) + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_expFlame_reg


```

For example, this is the same expBurn and expFlame plots as above, but faceted (grouped and separated) by priority and treatment type. 

```{r prioritytype, fig.width=pt_width, fig.height=pt_height, out.width="80%"}
plot_yr2039_expBurn_pt <- ggplot() + 
  geom_point(data=res2039_trim, 
             aes(x=expBurn_500k, y=expBurn_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) + 
  stat_smooth(data=res2039_trim,
              aes(x=expBurn_500k, y=expBurn_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE, 
              fullrange = TRUE) + 
  labs(title="Year 2039: Expected Burned Acres",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") +
  facet_wrap(~Priority+TxType) + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_expBurn_pt

plot_yr2039_expFlame_pt <- ggplot() + 
  geom_point(data=res2039_trim, 
             aes(x=expFlame_500k, y=expFlame_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) + 
  stat_smooth(data=res2039_trim,
              aes(x=expFlame_500k, y=expFlame_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE, 
              fullrange = TRUE) + 
  labs(title="Year 2039: Flame Index",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") +
  facet_wrap(~Priority+TxType) + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_expFlame_pt

```


### SC Region

We could want to only look at one region at a time, so we can add another filtering step to just look at South Coast (SC). 

```{r scregion}
#SC only
res2039sc <- res2039_trim %>% 
  filter(Region == "SC")
```

And then we can repeat our graphing, perhaps for both priority and treatment type. 

```{r scpt, fig.width=pt_width, fig.height=pt_height, out.width="80%"}
plot_yr2039_sc_expBurn_pt <- ggplot() + 
  geom_point(data=res2039sc, 
             aes(x=expBurn_500k, y=expBurn_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) + 
  stat_smooth(data=res2039sc,
              aes(x=expBurn_500k, y=expBurn_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE, 
              fullrange = TRUE) + 
  labs(title="SC: Year 2039: Expected Burned Acres",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") +
  facet_wrap(~Priority+TxType) + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_sc_expBurn_pt

plot_yr2039_sc_expFlame_pt <- ggplot() + 
  geom_point(data=res2039sc, 
             aes(x=expFlame_500k, y=expFlame_2m),
             shape=1, color="blue") +
  geom_abline(intercept=0, slope=1) + 
  stat_smooth(data=res2039sc,
              aes(x=expFlame_500k, y=expFlame_2m),
              method=lm,
              geom="smooth",
              formula = "y ~ x",
              se = FALSE, 
              fullrange = TRUE) + 
  labs(title="SC: Year 2039: Flame Index",
       x="500k Acres Treated",
       y="2.3 Million Acres Treated") +
  facet_wrap(~Priority+TxType) + 
  theme_bw() + 
  theme(aspect.ratio = 1)
plot_yr2039_sc_expFlame_pt
```

#### Boxplots 

Joint distribution plots are convenient for comparing two aspects against each other, but we can also graph some of the same information in different ways. To avoid too cluttered of charts, we may need to partition the dataset in some fashion (filtering or faceting). 

```{r scboxplot, out.width="75%"}

# Returning to original 2039 dataset
r39sc <- res2039 %>% 
  filter(Region == "SC") %>% 
  # Need a single field for labeling scenario
  mutate(scenario = paste0(Priority, " - ", 
                           TxIntensity, " - ", 
                           TxType),
         scenario_intensity_type = paste0(TxIntensity, " - ", TxType))

ggplot() +
  geom_boxplot(data=r39sc,
               mapping=aes(x=scenario_intensity_type, y=expBurn)) +
  labs(title="SC: Year 2039: Expected Burned Acres per HUC",
       x="Intensity - Treatment Type",
       y="Expected burned acres") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) + 
  facet_wrap(~Priority) 

ggplot() +
  geom_boxplot(data=r39sc,
               mapping=aes(x=scenario_intensity_type, y=expFlame)) +
  labs(title="SC: Year 2039: Flame Index per HUC",
       x="Intensity - Treatment Type",
       y="Expected total flame index") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) + 
  facet_wrap(~Priority)



```

Instead of individual HUC points, we may wish to add all burned area together, region-wide.

```{r scbargraph, out.width="75%"}

r39sc_summarized <- r39sc %>% 
  group_by(Priority, TxIntensity, TxType) %>% 
  summarize(sum_expBurn = sum(expBurn),
            .groups="drop") %>% 
  mutate(intensity_type = paste0(TxIntensity, " - ", TxType),
         priority_intensity = paste0(Priority, " - ", TxIntensity))

ggplot() +
  geom_col(data=r39sc_summarized,
           mapping=aes(x=intensity_type, y=sum_expBurn)) +
  labs(title="SC: Year 2039: Total Expected Burned Acres",
       x="Intensity - Treatment Type",
       y="Total expected burned acres") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) + 
  facet_wrap(~Priority)


```

Or reworking the summarizing and faceting, here is another way to view the same information. 

```{r scbar2, fig.width=pt_width, fig.height=pt_height, out.width="80%"}
r39sc_sum2 <- r39sc %>% 
  group_by(Priority, TxIntensity, TxType) %>% 
  summarize(sum_expBurn = sum(expBurn),
            .groups="drop")

ggplot() +
  geom_col(data=r39sc_sum2,
           mapping=aes(x=TxIntensity, y=sum_expBurn)) +
  labs(title="SC: Year 2039: Total Expected Burned Acres",
       x="Intensity",
       y="Total expected burned acres") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) + 
  facet_wrap(~Priority+TxType) 


```


## Timeseries (boxplots)

The above examples were exploring a timeslice, a single year. We may also want to look at the results over time. Let us select SC as our region, "Fire" as the priority, and "trt4" (heavy thinning without removal) as the treatment type. We will look at the three intensities over the four years. 

```{r tssetup}

#Select an example scenario
this_region <- "SC"
this_priority <- "Fire"
this_trt <- "trt4"
#create a new nice treatment label
trt_desc <- case_when(
  this_trt == "trt1" ~ "Moderate thinning biomass removal",
  this_trt == "trt4" ~ "Heavy thinning",
  this_trt == "trt6" ~ "Heavy Mastication", 
  this_trt == "trt7" ~ "Prescribed fire",
  .default = "Type not found") 

#We return to our results (res) before filtering on the year, 
# and filter to the selected
res_example <- res %>% 
  filter(Region == this_region,
         Priority == this_priority,
         TxType == this_trt) 

#Select the appropriate timing group for that Priority, per row
res_example <- res_example %>% 
  mutate(timing_group = case_when(
    Priority == "Fire" ~ timeFire, 
    Priority == "WUI" ~ timeWui,
    Priority == "Hybrid" ~ timeHybrid
  )) %>% 
  #and WUI 4th category is too long for graph displays
  mutate(timing_group = if_else(timing_group=="2024_2039_yr1to5_16to20",
                                "2024_2039",
                                timing_group))


#To ensure these years are displayed on graphs  
year_breaks <- c(2024, 2029, 2034, 2039) 

```

We will plot boxplots with the year along the x-axis and different metrics (expBurn and expFlame) on the y-axis. The graphs will facet on intensity and timing group. 

```{r tsplots, out.width="80%"}

# Note: the scales can either be fixed across all facets, or set per panel.
#  Fixed is nice that all axes are the same, but if there are large differences
#   in values, you may find that free_y produces better graphs. 
scales_box <- "fixed" #"free_y"

ggplot() +
  geom_boxplot(data = res_example,
               mapping = aes(x = Year, y = expBurn, group=Year)) +
  scale_x_continuous(breaks = year_breaks) +
  facet_wrap(~TxIntensity+timing_group, scales=scales_box) +
  labs(title = paste(this_region,
                     this_priority,
                     trt_desc)) + 
  theme_bw()

ggplot() +
  geom_boxplot(data = res_example,
               mapping = aes(x = Year, y = expFlame, group=Year)) +
  scale_x_continuous(breaks = year_breaks) +
  facet_wrap(~TxIntensity+timing_group, scales=scales_box) +
  labs(title = paste(this_region,
                     this_priority,
                     trt_desc)) + 
  theme_bw()

```

In the graphs above, the columns of graphs are the different timing groups (when that HUC was treated). The first column are HUCs that were treated in 2024. In their time series, you can see that the fire metrics start off the lowest in 2024, and increase as time passes. The second column was treated in 2029, and we can see the decrease in fire metrics in the 2029 boxplot of their time series.

## Time series (Line graphs)

We can also look at a time series of the average of all HUCs (irrespective of timing group). In the example below, we have selected a region and treatment type, and will show time series line graphs by priority (color) and intensity (line type). This way, we can somewhat compare scenarios of the same treatment type against each other. 

```{r tsline, out.width="75%"}

#Select an example trt
this_region <- "SC"
this_trt <- "trt4"

#create a new nice treatment label
trt_desc <- case_when(
  this_trt == "trt1" ~ "Moderate thinning biomass removal",
  this_trt == "trt4" ~ "Heavy thinning",
  this_trt == "trt6" ~ "Heavy Mastication", 
  this_trt == "trt7" ~ "Prescribed fire",
  .default = "Type not found") 

#We return to our results (res) before filtering on the year, 
# and filter to the selected
res_exline <- res %>% 
  filter(Region == this_region,
         TxType == this_trt) 

res_exline_mean <- res_exline %>% 
  group_by(Year, TxIntensity, Priority) %>% 
  #several options for metric
  summarize(ave_expBurn = mean(expBurn),
            sum_expBurn = sum(expBurn),
            ave_expFlame = mean(expFlame),
            ave_active = mean(expPcActive),
            .groups = "drop")

ggplot() +
  geom_line(data = res_exline_mean,
            mapping = aes(x=Year, y=ave_expFlame, 
                          color=Priority, linetype=TxIntensity)) +
  scale_x_continuous(breaks = year_breaks) +
  scale_color_manual("Priority", values = c("#b81267", "#4daf4a", "#377eb8")) +
  scale_linetype_manual("Intensity", values = c("solid", "dashed", "dotted")) +
  labs(title = paste(this_region,
                     trt_desc),
       y = "Mean of expFlame") + 
  theme_bw()


```

Here we can see that, in general, the 2m intensity treatments are better than 1m which are better than 500k, and that 1m and 500k start to blur in 2039. 

Similar graphs could be done by switching treatment type and priority around, such that for a particular priority, you can compare all treatment types and intensities. 

Note that this is collapsing all HUCs (averaging) so we are not seeing the variability of the HUCs within a scenario. We also may want to factor in treatment timing in more detailed analyses as well.  


## Maps and Best Scenarios

It is also possible to join the datacube data with spatial data to create maps. The HUC12 watershed spatial data is available as a shapefile or geopackage. 

```{r hiddenspatialread, include=FALSE, echo=FALSE}
hucs_spatial <- st_read(file.path("..", "..", 
                                  "results", "spatial", 
                                  "huc12_watersheds.gpkg"))
```

```{r spatialread, eval=FALSE}

#spatial data
hucs_spatial <- st_read("huc12_watersheds.gpkg"))

#For faster drawing in R, you can use a simplified version
# Uncomment and join with this later on instead of hucs_spatial
#hucs_simpl <- sf::st_simplify(hucs_spatial, preserveTopology = TRUE, dTolerance = 200)

#If CA state boundary wanted, download from 
# https://www.census.gov/geographies/mapping-files/time-series/geo/tiger-line-file.html
#states <- st_read("data/tl_2023_us_state/tl_2023_us_state.shp")
#ca <- states %>% filter(STUSPS == "CA")

```

Going back to our datacube results for a moment, for more descriptive labels on graphs or maps, we can create new variables based on the value in TxType. 

```{r trtlabel}

### relabeling trt --------------------------------

res <- res %>% 
  mutate(trt_desc = case_when(
    TxType == "trt1" ~ "Mod thin removal",
    TxType == "trt4" ~ "Heavy thinning",
    TxType == "trt6" ~ "Mastication", 
    TxType == "trt7" ~ "Prescribed fire",
    .default = "Type not found"
  ))

```

In this case, we will look at a simplified example of the average flame index (expFlame) over all years (2024, 2029, 2034, 2039). We will group our data by HUC and scenario (and notably not Year), then summarize to calculate the mean of expFlame. Then we arrange our dataset by the mean of expFlame and take the first (lowest) value per HUC12. This leaves us with a single row per HUC of the scenario that produced the lowest flame index for that HUC. 

```{r lowestflame}

### Lowest flame index, averaged over all years --------------

res_ave <- res %>% 
  # note, NOT by year, averaging over all years
  group_by(HUC12, Priority, TxIntensity, TxType, trt_desc) %>% 
  summarize(mean_expFlame = mean(expFlame),
            count_check = n(),
            .groups = "drop")


lowest_flame <- res_ave %>% 
  #by HUC
  group_by(HUC12) %>% 
  #take lowest
  slice_min(order_by=mean_expFlame, n=1)

```

By grouping and summarizing on different scenario aspects (priority, intensity, treatment type), we can count how many HUCs have the lowest flame index with that value. 

```{r bestflamecounts}

lowest_flame %>% 
  group_by(Priority) %>% 
  summarize(count = n())

lowest_flame %>% 
  group_by(TxIntensity) %>% 
  summarize(count = n())

lowest_flame %>% 
  group_by(trt_desc) %>% 
  summarize(count = n())

lowest_flame %>% 
  group_by(Priority, TxIntensity, trt_desc) %>% 
  summarize(count = n(), 
            .groups = "drop") %>% 
  arrange(desc(count)) 


#add scenario name
lowest_flame <- lowest_flame %>% 
  mutate(scenario_itp = paste0(TxIntensity, "-", trt_desc, "-", Priority))

```

Then we can join our spatial data to our lowest flame index dataset and prepare to create a map. 

```{r spatialjoin}
#add spatial data 

# If you are using a datacube with a subset of HUCs 
# use jan INNER join to only get hucs in this cube. 
# Otherwise, a left_join is the standard function used here. 
hucs_lowest <- hucs_spatial %>% 
  inner_join(lowest_flame,
             by = join_by("HUC12"))

```

We can map using R, as in the example below, but you may also wish to save the new spatial dataset to map in QGIS, ESRI ArcGIS, or other GIS software. 

```{r bestmap, fig.width=11, fig.height=9, out.width="100%"}

plot_best <- ggplot() +
  #California
  #geom_sf(data = ca, color = "grey50", fill = NA, size = 0.1) + 
  #HUCs
  geom_sf(data = hucs_lowest, 
          #color the HUC by scenario
          aes(fill = scenario_itp),
          color = "grey90", size = 0.01) +
  #use viridis color scheme
  scale_fill_viridis("Scenario", discrete=TRUE, option="viridis") + 
  #plot settings for a nicer map
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10),
        strip.background = element_blank(),
        strip.text = element_text(size = 13),
        axis.text = element_text(family = "sans"),
        legend.position = "right",
        legend.direction = "vertical") +
  #add a scale bar
  ggspatial::annotation_scale(
    location = "bl", bar_cols = c("grey50", "white")) +
  #add a north arrow
  ggspatial::annotation_north_arrow(
    location = "tr", which_north = "true",
    height = unit(0.6, "cm"), width = unit(0.6, "cm"),
    pad_x = unit(0.2, "in"), pad_y = unit(0.3, "in"),
    style = ggspatial::north_arrow_minimal()) +
  #add a plot title
  labs(title = "Best scenario by HUC12, 2024-2039")

plot_best

#Note: To change the order of the scenario legend items in R, we would need to create a 27-level ordered factor, similar to what we did near the beginning with setting a factor order on Priority and TxIntensity. 
# You may find it easier to do in QGIS where you can drag and drop to rearrange the order. 

#Here is how you could save out the dataset to use in another program. Note that shapefiles have character limits (eight) in the field name so some names might get truncated.
# st_write(hucs_lowest,
#          dsn="scenario_lowest_flame.gpkg", #geopackage, or .shp for shapefile
#          layer="scenario_lowest_flame")

```

